12th International Satisfiability Modulo Theories Competition (SMT-COMP 2017): Rules and Procedures

### 2017-04-20 rules/rules17.tex
Various updates for 2017

%\usepackage{draftwatermark}

@@

\title{11th International Satisfiability Modulo Theories Competition
  (SMT-COMP 2016): Rules and Procedures}

@@

\author{%
Sylvain Conchon \\
Paris-Sud University \\
France \\
{\small\href{mailto:Sylvain.Conchon@lri.fr}{\texttt{Sylvain.Conchon@lri.fr}}} \\
\and
David D{\'e}harbe \\
Clearsy, France \& Federal University\\ of Rio Grande do Norte, Brazil \\
{\small\href{mailto:david.deharbe@clearsy.com}{\texttt{david.deharbe@clearsy.com}}} \\
\and
Matthias Heizmann \\
University of Freiburg \\
Germany \\
{\small\href{mailto:heizmann@informatik.uni-freiburg.de}{\texttt{heizmann@informatik.uni-freiburg.de}}} \\
{\small\textsc{(Unsat Core Track)}} \\
\and
Tjark Weber \\
Uppsala University \\
Sweden \\
{\small\href{mailto:tjark.weber@it.uu.se}{\texttt{tjark.weber@it.uu.se}}} \\
\\
}

@@

\noindent Additional material will be made available at the
competition web site, \url{www.smtcomp.org} or
\url{smtcomp.sourceforge.net/2016}.

@@

\begin{description}
\item[May~1] Deadline for new benchmark contributions.
\item[May~15] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[May~22] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[May~29] Deadline for final versions of solvers, including
  system descriptions.
\item[May~30] Opening value of NYSE Composite Index used to complete
  random seed for benchmark scrambling.
\item[July~1/2] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

SMT-COMP~2016 is affiliated with the SMT Workshop~2016
(\url{http://smt-workshop.cs.uiowa.edu/2016/}), which is associated
with IJCAR~2016 (\url{http://ijcar-2016.info/}).  The SMT Workshop
will include a block of time to present the results of the
competition.

@@

SMT-COMP 2016 will have three tracks: the conventional main track, an
application (i.e., incremental) track, and an unsat-core track.  The
unsat-core track will be experimental in 2016.

@@

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Albert Oliveras, Aaron Stump, and Tjark Weber.} describes the rules
and competition procedures for SMT-COMP~2016.  The principal changes
from the previous competition rules are the following:
\begin{itemize}
\item Benchmarks will use (a subset of) version~2.5 of the SMT-LIB
  language.  \emph{Rationale:} This is the latest version of the
  SMT-LIB language.  It was released on 2015-06-28, and is largely
  backwards-compatible to version~2.0, which was used for SMT-COMP
  2015.
\item Solver output may affect the score even when the solver does not
  terminate within the time limit.  (In 2015, main track solver output
  was ignored if the solver subsequently timed out.)  Solvers should
  take care not to accidentally produce output that contains
  \texttt{sat} or \texttt{unsat} even when they are killed.
  \emph{Rationale:} Users are likely to trust solver responses even
  when the solver continues to run for some time.
\item Divisions for floating-point arithmetic are no longer
  experimental, and will be considered competitive if the necessary
  requirements (see Section~\ref{sec:scoring}) are met.
  \emph{Rationale:} Floating-point divisions were experimental in
  2015.  By now, their definition is sufficiently stable, and they are
  supported by several solvers.
\item Division scores will be based on a weighted sum of scores for
  benchmark families.  \emph{Rationale:} For some years now, SMT-COMPs
  have had sufficient computational resources to evaluate all solver
  entrants on all eligible benchmarks.  As a side-effect, the
  weighting of benchmark families that was achieved in early SMT-COMPs
  through a careful selection of benchmarks (based on benchmark
  difficulty and category) was lost.  Since there are vast differences
  in size between benchmark families, we believe that a weighting that
  de-emphasizes large benchmark families (see
  Section~\ref{sec:division-scoring}) will lead to more meaningful
  competition results.
\item The unsat-core track that was introduced in SMT-COMP 2012, but
  discontinued in 2013-2015 (partly because of the competition's move
  to StarExec), is back.  It will be experimental in 2016; its results
  will be reported, but no official winners will be announced.
  \emph{Rationale:} Unsat cores are important in many applications of
  SMT solving.  The track was discontinued primarily for
  infrastructure and resource reasons.  We are pleased that we can
  finally offer it again, but we ask for your understanding in case of
  mishaps while we port the required tools.
\item Best industrial performance will no longer be recognized
  separately.  \emph{Rationale:} While there is agreement in the SMT
  community to emphasize problems that come from real applications,
  industrial performance largely coincided with overall performance in
  SMT-COMP 2015.  We consider the effort to determine and report it
  separately no longer justified.
\end{itemize}

@@

\header{Solver submission.}
%
An entrant to SMT-COMP is an SMT solver submitted by its authors using
the StarExec (\url{http://www.starexec.org}) service.  The execution
service enables members of the SMT research community to run solvers
on jobs consisting of benchmarks from the SMT-LIB benchmark library.
Jobs are run on a shared computer cluster.  The execution service is
provided free of charge, but it does require registration to create a
login account.  Registered users may then upload their own solvers to
run, or may run public solvers already uploaded to the service.

For participation in SMT-COMP, a solver must be uploaded to StarExec,
made publicly available, and the organizers informed of its presence
\emph{and the tracks and divisions in which it is participating}.
StarExec supports solver configurations; for clarity, \emph{each
  submitted solver must have one configuration only}.  A submission
must also include a 32-bit unsigned integer.  These integer numbers,
collected from all submissions, are used to seed the benchmark
scrambler.

Information about how to configure and upload a solver is contained in
the StarExec user guide,
\url{https://wiki.uiowa.edu/display/stardev/User+Guide}.

@@

SMT-COMP entrants must be submitted via StarExec (solvers) \emph{and}
email to the organizers (accompanying information) until the end of
{\bf May~15, 2016} anywhere on earth.  After this date no new entrants
will be accepted.  However, updates to existing entrants on StarExec
will be accepted until the end of {\bf May~29, 2016} anywhere on
earth.

@@

\header{Dates of competition.}
%
The bulk of the computation will take place during the weeks leading
up to SMT~2016, from about May~30 to June~30.  Intermediate results
will be regularly posted to the SMT-COMP website as the competition
runs.

@@

The time limit~$T$ is yet to be determined, but it is anticipated to
be 40~minutes of wall-clock time per solver/benchmark
pair.\footnote{The time limit may be adjusted once we know the number
  of competition entrants and eligible benchmarks.}  Solvers that take
more than this time limit will be killed.  Solvers are allowed to
spawn other processes; these will be killed at approximately the same
time as the first started process.

@@

The main track competition uses a StarExec post-processor (named
``SMT-COMP 2016") to accumulate the results.

@@

\header{New benchmarks.}
%
The deadline for submission of new benchmarks is {\bf May~1, 2016}.
The organizers will be checking and curating these until {\bf May~22,
  2016}.  The organizers reserve the right to exclude new benchmarks
if any prove problematic for some reason.  SMT-COMP attempts to give
preference to benchmarks that are ``real-world,'' in the sense of
coming from or having some intended application outside SMT.

New benchmarks will be made publicly available as soon as possible
after the benchmark submission deadline, as they are checked and
curated.  The set of benchmarks selected for the competition will be
published when the competition begins.

@@

Each benchmark in SMT-LIB also has a \emph{category}.  There are four
possible categories:
\begin{itemize}
\item \emph{check.} These benchmarks are hand-crafted to test whether
  solvers support specific features of each division.
\item \emph{industrial.} These benchmarks come from some real
  application and are produced by tools such as bounded model
  checkers, static analyzers, extended static checkers, etc.
\item \emph{random.} These benchmarks are randomly generated.
\item \emph{crafted.} This category is for all other benchmarks.
  Usually, benchmarks in this category are designed to be particularly
  difficult or to test a specific feature of the logic.
\end{itemize}

\header{Benchmark selection.}
%
The benchmark pool is culled as follows:
\begin{enumerate}
\item \emph{Retire inappropriate benchmarks.} The competition
  organizers may remove from the eligibility pool certain benchmarks
  that are inappropriate\footnote{In 2016, this (again) includes all
    benchmarks that use partial or underspecified functions, e.g.,
    \texttt{bvudiv}, \texttt{fp.min}.}  or uninteresting for
  competition, or cut the size of certain benchmark families to avoid
  their over-representation.
\item \emph{Eliminate benchmarks whose status is unknown.} Any
  benchmark whose expected output is neither \texttt{sat} nor
  \texttt{unsat} is removed.  There are a significant number of
  benchmarks with \texttt{unknown} status in the library; these are
  certainly interesting and are a challenge to solve, but they are not
  used in the competition.\footnote{Incremental benchmarks may contain
    multiple \akey{check-sat} commands, each with its own status.
    Incremental benchmarks that contain (some) \akey{check-sat}
    commands with \texttt{unknown} status may still contain a prefix
    of commands where the status is known for all \akey{check-sat}
    commands in the prefix.  This prefix is eligible for the
    application track.}
\end{enumerate}
%
All remaining benchmarks are used for the competition.  There will be
no further selection of benchmarks, e.g., based on benchmark
difficulty or benchmark category.

\header{Heats.}
%
Since the organizers at this point are unsure how long a set of
benchmarks may take (which will depend also on the number of solvers
submitted), the competition may be run in \emph{heats}.  For each
track and division, the selected benchmarks may be randomly divided
into a number of (possibly unequal-sized) heats.  Heats will be run in
order.  If the organizers determine that there is adequate time, all
heats will be used for the competition.  Otherwise, incomplete heats
will be ignored.

@@

@@

\header{Main track.} More specifically, for the main track, we have
%
\begin{itemize}
\item $e=0$, $n=0$ if the solver aborts without a response, or the
  result of the \akey{check-sat} command is \texttt{unknown},
\item $e=0$, $n=1$ if the result of the \akey{check-sat} command is
  correct,
\item $e=1$, $n=0$ if the result of the \akey{check-sat} command is
  incorrect.
\end{itemize}
%
Note that a (correct or incorrect) response is taken into
consideration even when the solver process terminates abnormally, or
does not terminate within the time limit.  Solvers should take care
not to accidentally produce output that contains \texttt{sat} or
\texttt{unsat}.

@@

\subsection{Sequential performance}
\label{sec:sequential}

@@

@@

For a given competition benchmark~$b$, let~$F_b \geq 1$ be the total
number of benchmarks in $b$'s benchmark family that were used in the
competition track to which the division belongs.  We define the weight
for benchmark~$b$ as $\alpha_b = (1 + \log_e F_b) / F_b$.\footnote{See
  Section~\ref{sec:competition-wide} for a motivating discussion of
  log scaling.}  We define the \emph{normalized weight} for
benchmark~$b$ as $\alpha'_b = \alpha_b / (\sum_{b'} \alpha_{b'})$,
where the sum is over all benchmarks in the division.  Let~$N$ be the
total number of benchmarks in the division.

@@

\subsection{Competition-wide scoring}
\label{sec:competition-wide}

We define a competition-wide metric for the main track, separately for
parallel and sequential performance, as follows.  Let $N_i$ be the
total number of benchmarks in division~$i$ that were used in the
competition, and let $\langle e_i, n_i, w_i, c_i\rangle$ be a solver's
raw score for this division (Section~\ref{sec:division-scoring}).  The
solver's competition-wide raw score is $\sum_i (e_i == 0 \,?\,
(n_i/N_i)^2 : -e_i) \log_e N_i$, where the sum is over all competitive
divisions into which the solver was
entered.\footnote{\emph{Rationale:} This metric purposely emphasizes
  breadth of solver participation---a solver participating in many
  logics need not be the best in any one of them.  The use of the
  square in the metric limits that somewhat---a solver still needs to
  do reasonably well compared to winners to be able to catch up by
  breadth of participation.  The non-linear metric also gives added
  weight to completing close to all benchmarks in a division.  The log
  scaling is a (somewhat arbitrary) means to adjust the scores for the
  wide variety of numbers of benchmarks in different divisions.  It
  seems a reasonable compromise between linearly combining numbers of
  benchmarks, which would overweigh large divisions, and simply
  summing the fraction of benchmarks solved, which would overweigh
  small divisions.  The metric is also quite simple, and the metric
  for a solver is independent of the performance of other solvers.
  Time is omitted from the metric because it is only of third
  importance in the regular competition metric, and is difficult to
  compare across divisions.}  The solver's competition-wide sequential
score is computed from its sequential division scores
(Section~\ref{sec:division-scoring}) according to the same formula.
We will recognize the best three solvers according to these metrics.

@@

The organizers will also recognize the following contributions:
%
\begin{itemize}
\item \emph{Open source.}  The top solver that provides its source
  code as open source will be recognized in each competitive division.
\item \emph{Best new entrant}. The best performing entrant from a new
  solver implementation team, as measured by the competition-wide
  metric.
\item \emph{Breadth of logics}. Solvers that cover the most theories
  and logics.
\item \emph{Benchmarks}. Contributors of new benchmarks.
\end{itemize}
%
The organizers reserve the right to recognize other outstanding
contributions that become apparent in the competition results.

@@

\section{Acknowledgments and Disclaimer}

SMT-COMP 2016 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\begin{itemize}
\setlength{\itemsep}{0pt}
\item \href{https://www.lri.fr/~conchon/}{Sylvain Conchon}~--
  Paris-Sud University, France (co-organizer)
\item \href{https://www.sites.google.com/site/deharbe/}{David
  D{\'e}harbe}~-- Clearsy, France, and Federal University of Rio
  Grande do Norte, Brazil (co-organizer)
\item
  \href{https://swt.informatik.uni-freiburg.de/staff/heizmann}{Matthias
    Heizmann}~-- University of Freiburg, Germany (co-organizer, unsat
  core track)
\item \href{http://user.it.uu.se/~tjawe125/}{Tjark Weber}~-- Uppsala
  University, Sweden (chair)
\end{itemize}
%
Tjark Weber is responsible for policy and procedure decisions, such as
these rules, with input from the co-organizers. He is not associated
with any group creating or submitting solvers.

@@

David D{\'e}harbe is associated with the solver group producing the
veriT solver.  Matthias Heizmann is associated with the solver group
producing the SMTInterpol solver.

@@

%% Local Variables:
%% mode: latex
%% mode: flyspell
%% ispell-local-dictionary: "american"
%% LocalWords: arity Conchon logics satisfiability SMT Sylvain Tjark
%% End:

>>>>

\usepackage{draftwatermark}

\hyphenation{data-types}

@@

\title{12th International Satisfiability Modulo Theories Competition
  (SMT-COMP 2017): Rules and Procedures}

@@

\author{%
Matthias Heizmann \\
University of Freiburg \\
Germany \\
{\small\href{mailto:heizmann@informatik.uni-freiburg.de}{\texttt{heizmann@informatik.uni-freiburg.de}}} \\
\and
Giles Reger \\
University of Manchester \\
UK \\
{\small\href{mailto:giles.reger@manchester.ac.uk}{\texttt{giles.reger@manchester.ac.uk}}} \\
\and
Tjark Weber \\
Uppsala University \\
Sweden \\
{\small\href{mailto:tjark.weber@it.uu.se}{\texttt{tjark.weber@it.uu.se}}} \\
\\
}

@@

\noindent Additional material will be made available at the
competition web site, \url{www.smtcomp.org} or
\url{smtcomp.sourceforge.net/2017}.

@@

\begin{description}
\item[May~1] Deadline for new benchmark contributions.
\item[June~1] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[June~4] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[June~18] Deadline for final versions of solvers, including
  system descriptions.
\item[June~19] Opening value of NYSE Composite Index used to complete
  random seed for benchmark scrambling.
\item[July~22/23] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

SMT-COMP~2017 is part of the SMT Workshop~2017
(\url{http://smt-workshop.cs.uiowa.edu/2017/}), which is affiliated
with CAV~2017 (\url{http://cavconference.org/2017/}).  The SMT
Workshop will include a block of time to present the results of the
competition.

@@

SMT-COMP 2017 will have three tracks: the conventional main track, an
application (i.e., incremental) track, and an unsat-core track.

@@

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Albert Oliveras, Aaron Stump, and Tjark Weber.}
describes the rules and competition procedures for SMT-COMP~2017.  The
principal changes from the previous competition rules are the
following:
\begin{itemize}
\item Submission of accompanying information for solvers is via a web
  form (rather than by email to the organizers).  \emph{Rationale:}
  Email submissions were often incomplete, leading to ambiguity and
  further inquiries.  The form provides a more structured way of
  submitting information.
\item Benchmarks with unknown status will be eligible for the
  competition's main track.  In 2016, solver performance on benchmarks
  with unknown status was evaluated but reported separately; in 2017,
  it will directly affect the competition results.  \emph{Rationale:}
  Using only benchmarks with known status (i.e., benchmarks that have
  been solved before) to determine the competition results unjustly
  favors imitation of existing solvers over true innovation.
\item Benchmarks will likely use (a subset of) version~2.5 of the
  SMT-LIB language.  \emph{Rationale:} This is the latest version of
  the SMT-LIB language.  Its use had been announced for SMT-COMP 2016
  already, but was delayed because the SMT-LIB benchmark collection
  had not been updated.  Solvers should ideally support both
  versions~2.0 and~2.5; the latter is largely backwards-compatible.
\item Benchmarks that use partial bit-vector functions, such as
  \texttt{bvudiv}, may become eligible for the competition again,
  provided the semantics of these functions (according to SMT-LIB) is
  changed to agree with existing solver implementations, and the
  status of affected SMT-LIB benchmarks is updated accordingly.
  \emph{Rationale:} The semantics of these functions has been
  discussed for a long time, and it appears that a conclusion has
  finally been reached.
\item The penalty for erroneous results in the competition-wide
  scoring is changed from the number of errors to a fixed constant
  (multiplied by the weight of the respective division).
  \emph{Rationale:} The weight already takes the number of benchmarks
  in a division into account; multiplying it by the number of errors
  overemphasizes large divisions.
\item The unsat-core track, which was re-introduced in 2016, is no
  longer experimental.  Its divisions will be considered competitive
  if the necessary requirements (see Section~\ref{sec:scoring}) are
  met.  \emph{Rationale:} Rules and tool support for the unsat-core
  track proved sufficiently stable in 2016.
\item The competition may feature experimental divisions for
  benchmarks that use algebraic datatypes, provided suitable
  benchmarks are available.  \emph{Rationale:} Algebraic datatypes are
  specified in the draft SMT-LIB~2.6 standard, which is expected to
  become official in the near future, and are already supported by
  some solvers.
\end{itemize}

@@

\header{Solver submission.}
%
An entrant to SMT-COMP is an SMT solver submitted by its authors using
the StarExec (\url{http://www.starexec.org}) service.  The execution
service enables members of the SMT research community to run solvers
on jobs consisting of benchmarks from the SMT-LIB benchmark library.
Jobs are run on a shared computer cluster.  The execution service is
provided free of charge, but it does require registration to create a
login account.  Registered users may then upload their own solvers to
run, or may run public solvers already uploaded to the service.
Information about how to configure and upload a solver is contained in
the StarExec user guide,
\url{https://wiki.uiowa.edu/display/stardev/User+Guide}.

For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available.  StarExec supports solver configurations;
for clarity, \emph{each submitted solver must have one configuration
  only}.  Moreover, the organizers must be informed of the solver's
presence \emph{and the tracks and divisions in which it is
  participating} via the web form at
\begin{center}
  \url{https://goo.gl/forms/HL6rbOywqW4sFo1D2}
\end{center}
A submission must also include a 32-bit unsigned integer.  These
integer numbers, collected from all submissions, are used to seed the
benchmark scrambler.

@@

SMT-COMP entrants must be submitted via StarExec (solvers) \emph{and}
the above web form (accompanying information) until the end of {\bf
  June~4, 2017} anywhere on earth.  After this date no new entrants
will be accepted.  However, updates to existing entrants on StarExec
will be accepted until the end of {\bf June~18, 2017} anywhere on
earth.

@@

\header{Dates of competition.}
%
The bulk of the computation will take place during the weeks leading
up to SMT 2017.  Intermediate results will be regularly posted to the
SMT-COMP website as the competition runs.

@@

The time limit~$T$ is yet to be determined, but it is anticipated to
be at most 40~minutes of wall-clock time per solver/benchmark
pair.\footnote{The time limit may be adjusted once we know the number
  of competition entrants and eligible benchmarks.  Because of the
  inclusion of benchmarks with unknown status, the time limit may be
  lower than in previous years.}  Solvers that take more than this
time limit will be killed.  Solvers are allowed to spawn other
processes; these will be killed at approximately the same time as the
first started process.

@@

The main track competition uses a StarExec post-processor (named
``SMT-COMP 2017") to accumulate the results.

@@

\header{New benchmarks.}
%
The deadline for submission of new benchmarks is {\bf May~1, 2017}.
The organizers, in collaboration with the SMT-LIB maintainers, will be
checking and curating these until {\bf June~1, 2017}.  The SMT-LIB
maintainers intend to make a new release of the benchmark library
publicly available on or close to this date.

@@

\header{Benchmark selection.}
%
The competition will use a large subset of SMT-LIB benchmarks.  The
benchmark pool is culled as follows:
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The competition
  organizers may remove benchmarks that are deemed
  inappropriate\footnote{In 2017, this may (again) include all
    benchmarks that use partial or underspecified functions, e.g.,
    \texttt{bvudiv}, \texttt{fp.min}, unless their semantics can be
    resolved in time for the competition.}  or uninteresting for
  competition, or cut the size of certain benchmark families to avoid
  their over-representation.  SMT-COMP attempts to give preference to
  benchmarks that are ``real-world,'' in the sense of coming from or
  having some intended application outside SMT.
\item \emph{Remove incremental benchmarks whose first \akey{check-sat}
  command has unknown status.}  Incremental benchmarks may contain
  multiple \akey{check-sat} commands, each with its own status.  If an
  incremental benchmark contains a \akey{check-sat} command whose
  status is unknown, only the prefix of the benchmark up to the
  preceding \akey{check-sat} command is eligible for the application
  track of the competition; if the benchmark's first \akey{check-sat}
  command has unknown status, the entire benchmark is
  ineligible.\footnote{It might be desirable to also include
    \akey{check-sat} commands with unknown status in the application
    track (for the same reasons they are now included in the main
    track), but this would require substantial changes to the trace
    executor and scoring tools.}
\end{enumerate}
%
All remaining benchmarks are used for the competition.  There will be
no further selection of benchmarks, e.g., based on benchmark
difficulty or benchmark category.

The set of benchmarks selected for the competition will be published
when the competition begins.

\header{Heats.}
%
Since the organizers at this point are unsure how long the set of
benchmarks may take (which will depend also on the number of solvers
submitted), the competition may be run in \emph{heats}.  For each
track and division, the selected benchmarks may be randomly divided
into a number of (possibly unequal-sized) heats.  Heats will be run in
order.  If the organizers determine that there is adequate time, all
heats will be used for the competition.  Otherwise, incomplete heats
will be ignored.

@@

\subsection{Competitive divisions}

@@

\header{Main track.} More specifically, for the main track, we have
%
\begin{itemize}
\item $e=0$, $n=0$ if the solver aborts without a response, or the
  result of the \akey{check-sat} command is \texttt{unknown},
\item $e=0$, $n=1$ if the result of the \akey{check-sat} command is
  \texttt{sat} or \texttt{unsat}, and the result either agrees with
  the benchmark status or the benchmark status is unknown,\footnote{If
    the benchmark status is unknown, we thus treat the solver's answer
    as correct.  Disagreements between different solvers on benchmarks
    with unknown status are governed in
    Section~\ref{sec:division-scoring}.}
\item $e=1$, $n=0$ if the result of the \akey{check-sat} command is
  incorrect.
\end{itemize}
%
Note that a (correct or incorrect) response is taken into
consideration even when the solver process terminates abnormally, or
does not terminate within the time limit.  Solvers should take care
not to accidentally produce output that contains \texttt{sat} or
\texttt{unsat}.

@@

\subsection{Sequential performance (main track)}
\label{sec:sequential}

@@

\header{Main track: removal of disagreements.}
%
Before division scores are computed for the main track, benchmarks
with unknown status are removed from the competition results if two
(or more) sound solvers disagree on their result.  More specifically,
a solver (including a solver that was entered into the competition by
the organizers for comparison purposes) is \emph{sound} for a division
if its raw score (Section~\ref{sec:benchmark-scoring}) is of the form
$\langle 0, n, w, c\rangle$ for each benchmark in the division, i.e.,
if it did not produce any erroneous results.  Two solvers
\emph{disagree} on a benchmark if one of them reported \texttt{sat}
and the other reported \texttt{unsat}.  Only the remaining benchmarks
are used in the following computation of division scores.

\medskip

@@

For a given competition benchmark~$b$, let~$F_b \geq 1$ be the total
number of benchmarks in $b$'s benchmark family that were used in the
competition track to which the division belongs (and not removed
because of disagreements).  We define the weight for benchmark~$b$ as
$\alpha_b = (1 + \log_e F_b) / F_b$.\footnote{See
  Section~\ref{sec:competition-wide} for a motivating discussion of
  log scaling.}  We define the \emph{normalized weight} for
benchmark~$b$ as $\alpha'_b = \alpha_b / (\sum_{b'} \alpha_{b'})$,
where the sum is over all benchmarks in the division.  Let~$N$ be the
total number of benchmarks in the division.

@@

\subsection{Competition-wide scoring (main track)}
\label{sec:competition-wide}

We define a competition-wide metric for the main track, separately for
parallel and sequential performance, as follows.  Let $N_i$ be the
total number of benchmarks in division~$i$ that were used in the
competition (and not removed because of disagreements), and let
$\langle e_i, n_i, w_i, c_i\rangle$ be a solver's raw score for this
division (Section~\ref{sec:division-scoring}).  The solver's
competition-wide raw score is
%
$$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -4) \log_e N_i$$
%
where the sum is over all competitive divisions into which the solver
was entered.\footnote{\emph{Rationale:} This metric purposely
  emphasizes breadth of solver participation---a solver participating
  in many logics need not be the best in any one of them.  The use of
  the square in the metric limits this somewhat---a solver still needs
  to do reasonably well compared to winners to be able to catch up by
  breadth of participation.  The non-linear metric also gives added
  weight to completing close to all benchmarks in a division.

  The constant penalty for errors reflects the fact that any error (in
  a particular division) renders a solver untrustworthy for that
  division.  The value~$-4$ balances the community's interest in
  correct (thoroughly tested) solvers against the risk of stifling
  innovation: entering a perfect (but possibly buggy) solver into a
  division has a positive expected value if the probability of a
  soundness bug is below $\frac{1}{1+4} = 20$\,\%.

  The log scaling is a (somewhat arbitrary) means to adjust the scores
  for the wide variety of numbers of benchmarks in different
  divisions.  It seems a reasonable compromise between linearly
  combining numbers of benchmarks, which would overweigh large
  divisions, and simply summing the fraction of benchmarks solved,
  which would overweigh small divisions.

  The metric is also quite simple, and the metric for a solver is
  independent of the performance of other solvers.  Time is omitted
  from the metric because it is only of third importance in the
  regular competition metric, and is difficult to compare across
  divisions.}  The solver's competition-wide sequential score is
computed from its sequential division scores
(Section~\ref{sec:division-scoring}) according to the same formula.
We will recognize the best three solvers according to these metrics.

@@

The organizers will also recognize the following contributions:
%
\begin{itemize}
\item \emph{Best new entrant}. The best performing entrant from a new
  solver implementation team, as measured by the competition-wide
  metric.
\item \emph{Benchmarks}. Contributors of new benchmarks.
\end{itemize}
%
The organizers reserve the right to recognize other outstanding
contributions that become apparent in the competition results.

@@

\section{Acknowledgments}

SMT-COMP 2017 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\begin{itemize}
\setlength{\itemsep}{0pt}
\item \href{http://www.cs.man.ac.uk/~regerg/}{Giles Reger}~--
  University of Manchester, UK (co-organizer)
\item
  \href{https://swt.informatik.uni-freiburg.de/staff/heizmann}{Matthias
    Heizmann}~-- University of Freiburg, Germany (co-organizer)
\item \href{http://user.it.uu.se/~tjawe125/}{Tjark Weber}~-- Uppsala
  University, Sweden (chair)
\end{itemize}
%
Tjark Weber is responsible for policy and procedure decisions, such as
these rules, with input from the co-organizers. He is not associated
with any group creating or submitting solvers.

@@

\header{Disclosure.}
%
Matthias Heizmann is associated with the group producing the
SMTInterpol solver.  Giles Reger is associated with the group
producing the Vampire system.

@@

%% Local Variables:
%% mode: latex
%% mode: flyspell
%% ispell-local-dictionary: "american"
%% LocalWords: arity Heizmann logics Reger satisfiability SMT StarExec Tjark
%% End:
